Topic modeling on EU and the USA research projects

### 2017-06-18 thesis_report/draft_thesis.tex
Update: Topic evolution in USA

In figure x we show the 10 topics that consists of the 20 top words with the
highest posterior probability of belonging to the topic. The size of each word
is in proportion to each probability; the bigger the word, the higher the
probability. Each wordcloud describes a topic, which we can find intuitevely.
Below are listed the topics that we found corresponding to the words that
describe them:
\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic0_all.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic1_all.png}} &
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic2_all.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic3_all.png}} &
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic4_all.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic5_all.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic6_all.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic7_all.png}} &
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic8_all.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic9_all.png}} &
\end{tabular}
\caption{Wordclouds of topics of the EU dataset (1994-2017)}
\end{figure}
\end{center}

@@

@@

>>>>

In figure x we show the 10 topics that consists of the 20 top words with the
highest posterior probability of belonging to the topic. The size of each word
is in proportion to each probability; the bigger the word, the higher the
probability. Each wordcloud describes a topic, which we can find intuitevely.
Below are listed the topics that we found corresponding to the words that
describe them:
\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic0_all.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic1_all.png}} &
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic2_all.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic3_all.png}} &
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic4_all.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic5_all.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic6_all.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic7_all.png}} &
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic8_all.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic9_all.png}} &
\end{tabular}
\caption{Wordclouds of topics of the EU dataset (1994-2017)}
\end{figure}
\end{center}

@@

Just like the EU dataset, we found the 10 topics of the USA dataset from 1994 to
2016. Since, we're looking for the topic distribution over time, in this
implementation we took the projects per year (instead of using the separation of
the dataset per FP), to visualize the evolution of each topic per year. We ran
the LDA model with 12000 iterations and the dame value of the rest of the
parameters, as described in section 4.3.

Each one of the wordclouds in figure X represents a topic. The topics that are
described in the wordclouds are listed below:

\begin{itemize}
\item[] Topic 0: Material science and High energy physics
\item[] Topic 1: Mathematics
\item[] Topic 2: (Molecular) biology, Genetics
\item[] Topic 3: Science of social policy and economics
\item[] Topic 4: International research and conferences
\item[] Topic 5: Chemistry and Materials science
\item[] Topic 6: STEM education
\item[] Topic 7: Climatology, Atmospheric and Ocean sciences
\item[] Topic 8: Molecular biology 
\item[] Topic 9: Mechanical engineering
\end{itemize}

!!!Write what you computed to get the results

@@

\begin{center}
\begin{figure}
\includegraphics[width=1.0\textwidth, natwidth=707,natheight=483]
{figs/topic-evolution-usa.png}
\caption{Topics over time in USA}
\end{figure}
\end{center}
